% Quote command definitions
% These commands output the quote text with proper formatting

\newcommand{\quoteone}{%
\vspace{1.0\baselineskip}%
\begin{quote}\ttfamily
Spatial features encompass the two-dimensional geometric properties and spatial relationships of target objects, including their shapes and relative positions within the scene. While RGB imaging systems excel at capturing such spatial information, they exhibit limitations in acquiring structural features, which include three-dimensional surface profiles and the geometric composition of objects.%
\end{quote}%
\vspace{1.0\baselineskip}%
}

\newcommand{\quotetwo}{%
\vspace{1.0\baselineskip}%
\begin{quote}\ttfamily
A cat can remember, can understand the physical world, can plan complex actions, can do some level of reasoning—actually much better than the biggest LLMs. —Yann LeCunn (2024)%
\end{quote}%
\vspace{1.0\baselineskip}%
}

\newcommand{\quotethree}{%
\vspace{1.0\baselineskip}%
\begin{quote}\ttfamily
vision is the production of relevant uncluttered visual information representations of the external world. —Marr 1976, Marr et al 1978%
\end{quote}%
\vspace{1.0\baselineskip}%
}

\newcommand{\quotefour}{%
\vspace{1.0\baselineskip}%
\begin{quote}\ttfamily
AI is the science of making machines capable of performing tasks that would require intelligence if done by humans. —The Society of mind, Minsky, Marvin Lee, 1927 [13]%
\end{quote}%
\vspace{1.0\baselineskip}%
}

\newcommand{\quotefive}{%
\vspace{1.0\baselineskip}%
\begin{quote}\ttfamily
In the new setting of ideas, the distinction (between particles and waves) has vanished, because it was discovered that all particles have also wave properties, and vice-versa. Neither of the concepts must be discarded, they must be amalgamated. Which aspect obtrudes itself depends not on the physical object but on the experimental device set up to examine it. —Erwin Schrödinger (1867–1961). Science, Theory and Man (New York, Dover, 1957)%
\end{quote}%
\vspace{1.0\baselineskip}%
}

\newcommand{\quotesix}{%
\vspace{1.0\baselineskip}%
\begin{quote}\ttfamily
homogenization efficiency test is to determine if the instrument homogenizer is breaking fat globules down into small enough sizes to allow the instrument to give accurate test results without interference due to light scattering by large fat globules. —D. M. BARBANO et al, 1989%
\end{quote}%
\vspace{1.0\baselineskip}%
}

\newcommand{\quoteseven}{%
\vspace{1.0\baselineskip}%
\begin{quote}\ttfamily
… the Milko-tester (Foss Electric, Hillerød, Denmark) measured the Vis scattering after dispersion of the CN micelles and homogenization to produce a more uniform fat globule size distribution. —Aernouts et al., 2015%
\end{quote}%
\vspace{1.0\baselineskip}%
}
