\documentclass[11pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{times}

% Letter details - PLEASE UPDATE THESE WITH YOUR INFORMATION
\name{Your Name}
\address{Your Address\\City, Country}
\date{\today}

\begin{document}

\begin{letter}{Eminent Person's Name\\Title or Position\\Institution or Organization\\Address}

\opening{Dear Sir or Madam,}

I hope this letter finds you in good health and high spirits. I am writing to you with the utmost respect and humility to request your kind consideration in providing a letter of recommendation to support my application for the UK Global Talent visa.

As a doctoral candidate at the University of Edinburgh, I have had the privilege of advancing research that has resulted in both patent applications and publication drafts, demonstrating my contributions to the field. I am deeply honoured to have received the full and unwavering support of both the University of Edinburgh and my esteemed academic supervisor, Dr. Istvan Gyongy, who has graciously provided a comprehensive recommendation letter that I have attached for your review.

The intellectual property and scholarly work emerging from my doctoral research---encompassing both patents and forthcoming publications---reflects not only my current competence and expertise but also, I believe, my potential to make meaningful contributions to the academic and research landscape in the United Kingdom. These achievements, while modest, represent years of dedicated inquiry and form the foundation upon which I hope to build a career of scholarly excellence.

I must, with some trepidation, share that my current circumstances are marked by considerable urgency. At present, I have no source of income, and the successful outcome of this visa application is not merely a professional aspiration but a matter of personal survival. The opportunity to continue my research and contribute to the UK's academic community through the Global Talent visa would provide not only the stability I so desperately need but also the platform to realise the potential that my supervisors and institution have recognised in my work.

I understand that requests of this nature require careful consideration, and I would be profoundly grateful for any support you might be able to offer. Your endorsement would carry significant weight in the visa application process and would represent a transformative opportunity for my career and personal circumstances.

I have enclosed the recommendation letter from Dr. Istvan Gyongy, along with documentation of my patents and publication drafts, should you wish to review the evidence of my work and the support I have already received from my academic institution.

Thank you most sincerely for your time and consideration. I would be delighted to provide any additional information you might require and would welcome the opportunity to discuss my research and aspirations with you at your convenience.

\closing{With deepest respect and gratitude,}

\signature{Your Name}

\encl{Recommendation letter from Dr. Istvan Gyongy\\Patent documentation\\Publication drafts}

\end{letter}

\end{document}

