\documentclass[12pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{setspace}
\onehalfspacing

% Letter details
\name{Deborah Akuoko}

\begin{document}

\begin{letter}{Her Excellency Mrs. Sabah Zita Benson\\High Commissioner of Ghana to the United Kingdom and Ireland\\Ghana High Commission\\London\\UK}

\date{\today}

\opening{Dear Your Excellency,}

I hope this letter finds you well. I am writing to request your consideration in providing a letter of recommendation to support my application for the UK Global Talent visa.

I have already submitted my application with a comprehensive recommendation letter from my academic supervisor, Dr. Istvan Gyongy of the University of Edinburgh, and with the full support of the University itself. However, UK Visas and Immigration has responded to my application by requesting an additional letter of recommendation from an eminent person in the UK. This official request, which I have received via email, is attached for your review along with Dr. Gyongy's recommendation letter.

The reason I am approaching you, Your Excellency, is precisely because UKVI specifically requires a recommendation from an 'eminent' person based in the UK. By definition, an eminent person is one who has achieved distinguished recognition and standing in their field, typically evidenced by significant honours, leadership positions in prestigious institutions, and substantial contributions to their discipline. Your distinguished career exemplifies these criteria: as Ghana's first female High Commissioner to the United Kingdom and Ireland, having previously served as Minister of Information, Minister of Tourism, and Ambassador to the Czech Republic, you represent precisely the calibre of eminent person that UKVI seeks to provide such endorsements. Your standing in diplomatic and public service, combined with your commitment to improving the lives of Ghanaians—evident from your recent initiatives such as the "GH House" trade project designed to expand market access for Ghanaian products—demonstrates the leadership and vision that make you uniquely qualified to provide the authoritative assessment that UKVI requires.

Having recently submitted my PhD thesis at the University of Edinburgh, my research has resulted in both patent applications and publication drafts that demonstrate my contributions to the field. The intellectual property and scholarly work emerging from my doctoral research reflects my competence and expertise, as well as my potential to make meaningful contributions to the academic and research landscape in the United Kingdom.

I am particularly mindful that your support of my application to gain a visa in this country would go a long way to build expertise of Ghanaian origin. By enabling me to continue my research and professional development in the UK, your endorsement would contribute to the cultivation of highly skilled Ghanaian professionals who can eventually bring their knowledge, experience, and networks back to Ghana. This aligns with your vision of improving the lives of Ghanaians, as demonstrated through initiatives like GH House, by fostering the development of Ghanaian talent that can drive innovation, economic growth, and technological advancement in our homeland. The expertise I am building through my doctoral research and the professional opportunities that the Global Talent visa would afford me would ultimately serve to strengthen Ghana's capacity in science, technology, and research—contributing to the nation's development and the betterment of our people.

I must, with some trepidation, share that my current circumstances are marked by considerable urgency. At present, I have no source of income, and the successful outcome of this visa application is not merely a professional aspiration but a matter of personal survival. The prompt reception of the visa would go a long way to grant me financial opportunities that would enable me to help and support an ailing close relative who depends on my assistance. 

I must also acknowledge, with candour, that this matter has become more urgent for me than the completion of my PhD, for I cannot take pride in earning a prestigious degree when I find myself incapacitated as a result of having no right to work. The opportunity to continue my research and contribute to the UK's academic community through the Global Talent visa would provide not only the stability I so desperately need but also the platform to realise the potential that my supervisors and institution have recognised in my work.

I understand that requests of this nature require careful consideration, and I would be profoundly grateful for any support you might be able to offer. Your endorsement would carry significant weight in the visa application process and would represent a transformative opportunity for my career and personal circumstances, whilst also contributing to the development of Ghanaian expertise and capacity.

I have enclosed the UKVI email request, the recommendation letter from Dr. Istvan Gyongy, along with documentation of my patents and publication drafts, should you wish to review the evidence of my work and the support I have already received from my academic institution.

Thank you most sincerely for your time and consideration. I would be delighted to provide any additional information you might require and would welcome the opportunity to discuss my research and aspirations with you at your convenience.

\closing{With deepest respect and gratitude,}

\signature{Deborah Akuoko}

\encl{UKVI email request for additional recommendation\\Recommendation letter from Dr. Istvan Gyongy\\Patent documentation\\Publication drafts}

\end{letter}

\end{document}

