\documentclass[12pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{setspace}
\onehalfspacing

% Letter details
\name{Deborah Akuoko}

\begin{document}

\begin{letter}{Dr. Joseph Thom\\Challenge Manager\\NATO Defence Innovation Accelerator for the North Atlantic (DIANA)\\DIANA Headquarters\\London\\United Kingdom}

\date{\today}

\opening{Dear Dr. Thom,}

I hope this letter finds you well. I am writing to request your consideration in providing a letter of recommendation to support my application for the UK Global Talent visa.

I have already submitted my application with a comprehensive recommendation letter from my academic supervisor, Dr. Istvan Gyongy of the University of Edinburgh, and with the full support of the University itself. However, UK Visas and Immigration has responded to my application by requesting an additional letter of recommendation from an eminent person in the UK. This official request, which I have received via email, is attached for your review along with Dr. Gyongy's recommendation letter.

The reason I am approaching you, Dr. Thom, is precisely because UKVI specifically requires a recommendation from an 'eminent' person based in the UK. By definition, an eminent person is one who has achieved distinguished recognition and standing in their field, typically evidenced by significant honours, leadership positions in prestigious institutions, and substantial contributions to their discipline. Your distinguished career exemplifies these criteria: as Challenge Manager at NATO's Defence Innovation Accelerator for the North Atlantic (DIANA), and as an expert in optics with a deep understanding of emerging and disruptive technologies, you represent precisely the calibre of eminent person that UKVI seeks to provide such endorsements. Your standing in the UK scientific and defence innovation community, combined with your extensive expertise in optics and your role in identifying and accelerating breakthrough technologies for NATO, makes you uniquely qualified to provide the authoritative assessment that UKVI requires.

I am particularly moved to reach out to you because of the direct relevance of my research to your field of expertise in optics. As a doctoral candidate at the University of Edinburgh, I have recently submitted my PhD thesis, and my research has resulted in both patent applications and publication drafts that demonstrate my contributions to the field. Most significantly, as my academic supervisor Dr. Istvan Gyongy has testified in his recommendation letter, my research has the potential to make meaningful contributions to the advancement of optics. The intellectual property and scholarly work emerging from my doctoral research reflects not only my current competence and expertise but also, I believe, my potential to contribute to the field of optics in ways that could benefit both academic research and practical applications, including those relevant to defence and security technologies that DIANA seeks to advance.

I must, with some trepidation, share that my current circumstances are marked by considerable urgency. At present, I have no source of income, and the successful outcome of this visa application is not merely a professional aspiration but a matter of personal survival. The prompt reception of the visa would go a long way to grant me financial opportunities that would enable me to help and support an ailing close relative who depends on my assistance. 

I must also acknowledge, with candour, that this matter has become more urgent for me than the completion of my PhD, for I cannot take pride in earning a prestigious degree when I find myself incapacitated as a result of having no right to work. The opportunity to continue my research and contribute to the UK's academic and innovation community through the Global Talent visa would provide not only the stability I so desperately need but also the platform to realise the potential that my supervisors and institution have recognised in my work, particularly in advancing the field of optics.

I understand that requests of this nature require careful consideration, and I would be profoundly grateful for any support you might be able to offer. Your endorsement would carry significant weight in the visa application process and would represent a transformative opportunity for my career and personal circumstances.

I have enclosed the UKVI email request, the recommendation letter from Dr. Istvan Gyongy (which includes his testimony regarding the potential of my research to contribute to optics), along with a single document briefing my working papers and patents, should you wish to review the evidence of my work and the support I have already received from my academic institution.

Thank you most sincerely for your time and consideration. I would be delighted to provide any additional information you might require and would welcome the opportunity to discuss my research and its potential applications in optics with you at your convenience.

\closing{With deepest respect and gratitude,}

\signature{Deborah Akuoko}

\encl{UKVI email request for additional recommendation\\Recommendation letter from Dr. Istvan Gyongy\\Document briefing working papers and patents}

\end{letter}

\end{document}

