\documentclass[12pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{setspace}
\onehalfspacing

% Letter details
\name{Deborah Akuoko}

\begin{document}

\begin{letter}{Professor Sir Peter Mathieson\\Principal and Vice-Chancellor\\The University of Edinburgh\\Old College\\South Bridge\\Edinburgh\\EH8 9YL\\United Kingdom}

\date{\today}

\opening{Dear Professor Sir Peter Mathieson,}

I hope this letter finds you well. I am writing to request your consideration in providing a letter of recommendation to support my application for the UK Global Talent visa.

I have already submitted my application with a comprehensive recommendation letter from my academic supervisor, Dr. Istvan Gyongy of the University of Edinburgh, and with the full support of the University itself. However, UK Visas and Immigration has responded to my application by requesting an additional letter of recommendation from an eminent person in the UK. This official request, which I have received via email, is attached for your review along with Dr. Gyongy's recommendation letter.

The reason I am approaching you, Professor Mathieson, is precisely because UKVI specifically requires a recommendation from an 'eminent' person based in the UK. By definition, an eminent person is one who has achieved distinguished recognition and standing in their field, typically evidenced by significant honours, leadership positions in prestigious institutions, and substantial contributions to their discipline. Your distinguished service as Principal and Vice-Chancellor of the University of Edinburgh since February 2018, your role in conferring degrees on behalf of the Chancellor, your leadership of one of the world's most prestigious universities, and your extensive contributions to higher education and medical research—evidenced by your knighthood for services to higher education in 2023, your fellowships including FRCP, FRCPE, FMedSci, FRSE, and FRSA, and your previous role as President of the University of Hong Kong—exemplify precisely the calibre of eminent person that UKVI seeks to provide such endorsements. Your standing in the United Kingdom and internationally, combined with your commitment to academic excellence and research, makes you uniquely qualified to provide the authoritative assessment that UKVI requires.

I am particularly moved to reach out to you because of our direct connection through the University of Edinburgh. As Principal and Vice-Chancellor, you are responsible for the overall operation of the University and serve as President of the Senatus Academicus. As a current doctoral candidate at Edinburgh, I have had the privilege of pursuing my research under the auspices of this esteemed institution, and I believe that your understanding of the University's values, mission, and commitment to academic excellence would enable you to appreciate the significance of the work I have undertaken there. Having recently submitted my PhD thesis at the University of Edinburgh, my research has resulted in both patent applications and publication drafts that demonstrate my contributions to the field. The intellectual property and scholarly work emerging from my doctoral research reflects my competence and expertise, as well as my potential to make meaningful contributions to the academic and research landscape in the United Kingdom.

I must, with some trepidation, share that my current circumstances are marked by considerable urgency. At present, I have no source of income, and the successful outcome of this visa application is not merely a professional aspiration but a matter of personal survival. The prompt reception of the visa would go a long way to grant me financial opportunities that would enable me to help and support an ailing close relative who depends on my assistance. 

I must also acknowledge, with candour, that this matter has become more urgent for me than the completion of my PhD, for I cannot take pride in earning a prestigious degree when I find myself incapacitated as a result of having no right to work. The opportunity to continue my research and contribute to the UK's academic community through the Global Talent visa would provide not only the stability I so desperately need but also the platform to realise the potential that my supervisors and institution have recognised in my work.

I understand that requests of this nature require careful consideration, and I would be profoundly grateful for any support you might be able to offer. Your endorsement would carry significant weight in the visa application process and would represent a transformative opportunity for my career and personal circumstances.

I have enclosed the UKVI email request, the recommendation letter from Dr. Istvan Gyongy, along with a single document briefing my working papers and patents, should you wish to review the evidence of my work and the support I have already received from my academic institution.

Thank you most sincerely for your time and consideration. I would be delighted to provide any additional information you might require.

\closing{Yours sincerely,}

\signature{Deborah Akuoko}

\encl{UKVI email request for additional recommendation\\Recommendation letter from Dr. Istvan Gyongy\\Document briefing working papers and patents}

\end{letter}

\end{document}

